{Automatic Least-Effort Contextual Learning}

### 2017-03-02 etc/paper.tex
removed copycat and L-system citations
added subsection on Learning Grammars

\begin{table}[h]
  \begin{center}
  \begin{tabular}{|l|p{4in}|}
    \hline
    {\tt Get() \{Item\}}     & Yields the set of items in the active context \\
                               \hline
    {\tt Explore() \{Item\}} & Yields the set of items within one edge of
                               the active context \\ \hline
    {\tt Orient(ID)}         & Shifts context to focus on the item identified
                               by the given ID \\ \hline
    {\tt Add(Item)}          & Adds an item to the knowledge network \\ \hline
  \end{tabular}
  \end{center}
\caption{Methods on an instance of the knowledge network.}
\label{tab:sf_get}
\end{table}

The SKN system implements a knowledge abstraction, on par with typical
non-hierarchical sets or addressed memory. We refer to a small motivated
subnet of the knowledge network as the {\em context}. We provide a simple
interface for interacting with knowledge where all interactions either
retrieve information related to the current context or adjust the context
within the knowledge network, outlined in Table \ref{tab:sf_get}, where {\tt
Item} is a structure containing a unique identifier, a symbolic tag denoting
which mechanism can understand the item's content, and the arbitrary content
itself. Only the {\tt Add} and {\tt Orient} methods have the potential to
augment the active context. The context itself is sized according to the
maximum degree of a node in a scale-free network, based on network size $N$
and degree exponent $\gamma$ satisfying $2<\gamma<3$:
\[k_{\text{max}} \sim N^{\frac1{\gamma-1}}\]
The {\tt Add} method automatically adds a new item of
knowledge to the network, and adjusts the context to include the new item,
illustrated in Figure \ref{fig:sf_add}.

@@

We augment an algorithm which performs search on a learned expressive
grammar, the EC algorithm \cite{dechter13}. The augmentation will define the
grammar based on learned language artifacts stored in the context, rather
than artifacts stored in a small bounded set. The augmented EC algorithm
will be tested in the domain of string transformation, chosen because it has
potential for common underlying structure between tasks. Results will be
compared to the original EC algorithm.

This section is very much {\bf TODO}.

\section{Conclusion}

We introduce SKN, a knowledge abstraction to improve learning mechanisms by
utilizing context in a scale-free network, with the purpose of better
modeling memory and knowledge in a convenient paradigm that fits both the
intuitive architecture of cognition and the programmatic methods of
computation that govern technology.

\section{Future Work}

@@

  \bibitem{hofstadter94}
    Hofstadter, D. R., \& Mitchell, M. (1994).
    The copycat project: A model of mental fluidity and analogy-making.
    \emph{Advances in connectionist and neural computation theory}, 2(31-112), 29-30.
  \bibitem{rozenberg80}
    Rozenberg, G., \& Salomaa, A. (1980).
    Mathematical Theory of L systems.
    \emph{Academic Press, Inc.}.

>>>>

\begin{table}[h]
  \begin{center}
  \begin{tabular}{|l|p{4in}|}
    \hline
    {\sc Get() $\{\mathcal{I}\}$}     & Yields the set of items in the
      active context \\ \hline
    {\sc Explore() $\{\mathcal{I}\}$} & Yields the set of items within one
      edge of the active context \\ \hline
    {\sc Orient($\mathcal{I}$)}       & Shifts context to focus on the given
      item \\ \hline
    {\sc Add($\mathcal{I}$)}          & Adds an item to the knowledge
      network \\ \hline
  \end{tabular}
  \end{center}
\caption{Methods on an instance of the knowledge network.}
\label{tab:sf_get}
\end{table}

The SKN system implements a knowledge abstraction, on par with typical
non-hierarchical sets or addressed memory. We refer to a small motivated
subnet of the knowledge network as the {\em context}. We provide a simple
interface for interacting with knowledge where all interactions either
retrieve information related to the current context or adjust the context
within the knowledge network, outlined in Table \ref{tab:sf_get}, where
$\mathcal{I}$ refers to a knowledge artifact and is a structure containing a
unique identifier, a symbolic tag denoting which mechanism can understand
the item's content, and the arbitrary content itself. Only the {\sc
Add($\mathcal{I}$)} and {\sc Orient($\mathcal{I}$)} methods have the
potential to augment the active context. The context itself is sized
according to the maximum degree of a node in a scale-free network, based on
network size $N$ and degree exponent $\gamma$ satisfying $2<\gamma<3$:
\[k_{\text{max}} \sim N^{\frac1{\gamma-1}}\] The {\sc Add($\mathcal{I}$)}
method automatically adds a new item of knowledge to the network, and
adjusts the context to include the new item, illustrated in Figure
\ref{fig:sf_add}.

@@

\subsection{Learning Grammars}
We augment an algorithm which performs search on a learned expressive
grammar, the EC algorithm \cite{dechter13}. The augmentation defines the
grammar based on learned language artifacts stored in the context, rather
than artifacts stored in a small bounded set. We use SKN iteratively and
refer to the complete set of tasks as the {\em curriculum}, and each
iteration as a {\em phase}. Within each phase lies a set of tasks used with
a number of iterations of the EC algorithm. At the end of each phase, we
interact with the knowledge network.

The initial grammar employed by the EC algorithm at the beginning of each
phase is defined using the set of combinators in the current context:
\[C = \bigcup\text{\sc Get()} = \bigcup_{i=1}^k\mathcal{I}_i\]
At the end of each phase, we must determine whether the context should be
adjusted (and if so, where to adjust it) and whether to add a new knowledge
artifact. We refer to the new set of combinators constructed by the grammar
learner as $C^*$.

Consider the the set of combinators beyond the context:
\[C' = \bigcup\text{\sc Explore()}\]
If the most probable combinator $c_i$ in $C^*$ is also in $C'$, we adjust
the context according to the knowledge artifact which contains $c_i$:
\[\exists\mathcal{I}.\mathcal{I}\in\text{\sc Explore()}.c_i\in\mathcal{I}.\text{\sc Orient($\mathcal{I}$)}\]
We now recompute $C'$ with the new state of the knowledge network. We check
the $P$ most probable combinators in $C^*$, referred to as $C^P\subseteq
C^*$, for presence in $C'$, and add a new knowledge artifact with every
combinator not in $C'$:
\[\exists\mathcal{I}.\left(\mathcal{I}=C^P\setminus C'\right).
  |\mathcal{I}|>0.\text{\sc Add($\mathcal{I}$)}\]

The resulting system, parameterized by $P$, is such that the current context
may appropriately be identified as domain-specific knowledge, where a
knowledge artifact is a set of combinators which are used as primitives for
a grammar defined on the context.

The augmented EC algorithm will be tested in the domain of string
transformation, chosen because it has potential for common underlying
structure between tasks. This section is very much {\bf TODO} (needs
results).

\section{Discussion}

We introduce SKN, a knowledge abstraction to improve learning mechanisms by
utilizing context in a scale-free network, with the purpose of better
modeling memory and knowledge in a convenient paradigm that fits both the
intuitive architecture of cognition and the programmatic methods of
computation, enabling compositionality and the rapid learning of rich
models.

@@

%  \bibitem{hofstadter94}
%    Hofstadter, D. R., \& Mitchell, M. (1994).
%    The copycat project: A model of mental fluidity and analogy-making.
%    \emph{Advances in connectionist and neural computation theory}, 2(31-112), 29-30.
%  \bibitem{rozenberg80}
%    Rozenberg, G., \& Salomaa, A. (1980).
%    Mathematical Theory of L systems.
%    \emph{Academic Press, Inc.}.
